ADS Thesis simulation

### 2021-09-14 ads_thesis/simulation_replication.Rmd
Add ads thesis replication.

```{r}
data_url <- "https://raw.githubusercontent.com/gerkovink/Synthetic_ADS/main/Data/diabetes.csv"
data <- read_csv(url(data_url), 
                 col_types = cols(Pregnancies = col_integer(), 
                                  Glucose = col_integer(), 
                                  BloodPressure = col_integer(), 
                                  SkinThickness = col_integer(), 
                                  Insulin = col_integer(), 
                                  Age = col_integer(), 
                                  Outcome = col_factor(levels = c("1", "0"))))

data <- data[!data$BMI == 0,]
```

@@

```{r}
fit <- glm(Outcome ~ Pregnancies + Glucose + BMI, 
           family = binomial(link = "logit"), 
           data = data)

@@

```{r, cache = TRUE, cache.lazy = FALSE}
nsim <- 100
plan(multisession)

syn1 <- future_map(1:nsim, function(x) {
  data %>%
    mice(m = 5,
         method = mod1,
         predictorMatrix = pred,
         where = matrix(TRUE, nrow(.), ncol(.)),
         print = FALSE)
}, .options = future_options(seed = as.integer(123)), .progress = FALSE)

syn1_maxit1 <- future_map(1:nsim, function(x) {
  data %>%
    mice(m = 5, 
         maxit = 1,
         method = mod1,
         predictorMatrix = pred,
         where = matrix(TRUE, nrow(.), ncol(.)),
         print = FALSE)
}, .options = future_options(seed = as.integer(123)), .progress = FALSE)
```

```{r, cache = TRUE, cache.lazy = FALSE}
syn2 <- future_map(1:nsim, function(x) {
  data %>%
    mice(m = 5,
         method = mod2,
         predictorMatrix = pred,
         where = matrix(TRUE, nrow(.), ncol(.)),
         print = FALSE)
}, .options = future_options(seed = as.integer(123)), .progress = FALSE)

syn2_maxit1 <- future_map(1:nsim, function(x) {
  data %>%
    mice(m = 5, 
         maxit = 1,
         method = mod2,
         predictorMatrix = pred,
         where = matrix(TRUE, nrow(.), ncol(.)),
         print = FALSE)
}, .options = future_options(seed = as.integer(123)), .progress = FALSE)
```

```{r, cache = TRUE, cache.lazy = FALSE}
syn2_cp <- future_map(1:nsim, function(x) {
  data %>%
    mice(m = 5,
         method = mod2,
         predictorMatrix = pred,
         where = matrix(TRUE, nrow(.), ncol(.)),
         cp = 1e-32,
         minbucket = 3,
         print = FALSE)
}, .options = future_options(seed = as.integer(123)), .progress = FALSE)

syn2_cp_maxit1 <- future_map(1:nsim, function(x) {
  data %>%
    mice(m = 5, 
         maxit = 1,
         method = mod2,
         predictorMatrix = pred,
         where = matrix(TRUE, nrow(.), ncol(.)),
         cp = 1e-32,
         minbucket = 3,
         print = FALSE)
}, .options = future_options(seed = as.integer(123)), .progress = FALSE)
```

@@

```{r}
syn1 %>%
  map(function(x) {
    x %$% 
      glm(Outcome ~ Pregnancies + Glucose + BMI, 
          family = binomial(link = "logit"))
    }) %>%
  map_dfr(pool3.syn) %>%
  ci_cov(., fit) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

syn1_maxit1 %>%
  map(function(x) {
    x %$% 
      glm(Outcome ~ Pregnancies + Glucose + BMI, 
          family = binomial(link = "logit"))
    }) %>%
  map_dfr(pool3.syn) %>%
  ci_cov(., fit) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

```{r}
syn2 %>%
  map(function(x) {
    x %$% 
      glm(Outcome ~ Pregnancies + Glucose + BMI, 
          family = binomial(link = "logit"))
    }) %>%
  map_dfr(pool3.syn) %>%
  ci_cov(., fit) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

syn2_maxit1 %>%
  map(function(x) {
    x %$% 
      glm(Outcome ~ Pregnancies + Glucose + BMI, 
          family = binomial(link = "logit"))
    }) %>%
  map_dfr(pool3.syn) %>%
  ci_cov(., fit) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

```{r}
syn2_cp %>%
  map(function(x) {
    x %$% 
      glm(Outcome ~ Pregnancies + Glucose + BMI, 
          family = binomial(link = "logit"))
    }) %>%
  map_dfr(pool3.syn) %>%
  ci_cov(., fit) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

syn2_cp_maxit1 %>%
  map(function(x) {
    x %$% 
      glm(Outcome ~ Pregnancies + Glucose + BMI, 
          family = binomial(link = "logit"))
    }) %>%
  map_dfr(pool3.syn) %>%
  ci_cov(., fit) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

>>>>

```{r}
data_url <- "https://raw.githubusercontent.com/gerkovink/Synthetic_ADS/main/Data/diabetes.csv"
data <- read_csv(url(data_url), 
                 col_types = cols(Pregnancies = col_integer(), 
                                  Glucose = col_integer(), 
                                  BloodPressure = col_integer(), 
                                  SkinThickness = col_integer(), 
                                  Insulin = col_integer(), 
                                  Age = col_integer(), 
                                  Outcome = col_factor(levels = c("0", "1"))))
```

@@

```{r}
fit <- glm(Outcome ~ BMI + Glucose + Pregnancies, 
           family = binomial(link = "logit"), 
           data = data)

@@

```{r, cache = TRUE, cache.lazy = FALSE}
nsim <- 500
plan(multisession)
```

```{r, cache = TRUE, cache.lazy = FALSE}
syn2_maxit1 <- future_map(1:nsim, function(x) {
  data %>%
    mice(m = 5, 
         maxit = 1,
         method = mod2,
         predictorMatrix = pred,
         where = matrix(TRUE, nrow(.), ncol(.)),
         print = FALSE)
}, .options = future_options(seed = as.integer(123)), .progress = FALSE)
```

```{r, cache = TRUE, cache.lazy = FALSE}
syn2_cp_maxit1 <- future_map(1:nsim, function(x) {
  data %>%
    mice(m = 5, 
         maxit = 1,
         method = mod2,
         predictorMatrix = pred,
         where = matrix(TRUE, nrow(.), ncol(.)),
         cp = 1e-32,
         minbucket = 3,
         print = FALSE)
}, .options = future_options(seed = as.integer(123)), .progress = FALSE)
```

@@

```{r}
syn2_maxit1 %>%
  map(function(x) {
    x %$% 
      glm(Outcome ~ BMI + Glucose + Pregnancies, 
          family = binomial(link = "logit"))
    }) %>%
  map_dfr(pool3.syn) %>%
  ci_cov(., fit) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

```{r}
syn2_cp_maxit1 %>%
  map(function(x) {
    x %$% 
      glm(Outcome ~ BMI + Glucose + Pregnancies, 
          family = binomial(link = "logit"))
    }) %>%
  map_dfr(pool3.syn) %>%
  ci_cov(., fit) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

```{r, cache = TRUE, cache.lazy = FALSE}
syn2_boot <- future_map(1:nsim, function(x) {
  data[sample(1:nrow(data), replace = TRUE), ] %>%
    mice(m = 10, 
         maxit = 1,
         method = mod2,
         predictorMatrix = pred,
         where = matrix(TRUE, nrow(.), ncol(.)),
         cp = 0.0001,
         minbucket = 3,
         print = FALSE)
}, .options = future_options(seed = as.integer(123)), .progress = FALSE)

syn2_cp_boot <- future_map(1:nsim, function(x) {
  data[sample(1:nrow(data), replace = TRUE), ] %>%
    mice(m = 5, 
         maxit = 1,
         method = mod2,
         predictorMatrix = pred,
         where = matrix(TRUE, nrow(.), ncol(.)),
         cp = 1e-32,
         minbucket = 3,
         print = FALSE)
}, .options = future_options(seed = as.integer(123)), .progress = FALSE)

true_fits <- map(1:nsim, ~glm(Outcome ~ BMI + Glucose + Pregnancies,
                 family = binomial(link = "logit"), data = data[sample(1:nrow(data), replace = TRUE),]))

map_dfr(true_fits, function(x) {
  x %>% broom::tidy(conf.int = TRUE) %>% mutate(cov = conf.low < coef(fit) & coef(fit) < conf.high)
}) %>% 
  group_by(term) %>%
  summarise(est = mean(estimate),
                 se  = mean(std.error),
                 ciw = mean(conf.high - conf.low),
                 cov = mean(cov)) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

syn2_boot %>%
     map(function(x) {
    x %$% 
      glm(Outcome ~ BMI + Glucose + Pregnancies, 
          family = binomial(link = "logit"))
    }) %>%
  map_dfr(pool3.syn) %>%
  ci_cov(., fit) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

syn2_cp_boot %>%
   map(function(x) {
    x %$% 
      glm(Outcome ~ BMI + Glucose + Pregnancies, 
          family = binomial(link = "logit"))
    }) %>%
  map_dfr(pool3.syn) %>%
  ci_cov(., fit) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

# Zero's replaced by imputation

```{r, cache=TRUE, cache.lazy=FALSE}
data.imp <- 
  data %>%
  lapply(FUN = function(x) {
  ifelse(is.numeric(x) & x == 0, NA, x)
  }) %>%
  as.data.frame() %>%
  mutate(Outcome = factor(Outcome, labels = c("0", "1"))) %>%
  mice(m = 1, maxit = 50, method = "pmm") %>%
  complete()

fit.imp <- glm(Outcome ~ BMI + Glucose + Pregnancies,
               family = binomial(link = "logit"),
               data = data.imp)

syn2.boot.imp <- future_map(1:nsim, function(x) {
  data.imp[sample(1:nrow(data.imp), replace = TRUE), ] %>%
    mice(m = 10, 
         maxit = 1,
         method = mod2,
         predictorMatrix = pred,
         where = matrix(TRUE, nrow(.), ncol(.)),
         cp = 0.0001,
         minbucket = 3,
         print = FALSE)
}, .options = future_options(seed = as.integer(123)), .progress = FALSE)

syn2.cp.boot.imp <- future_map(1:nsim, function(x) {
  data.imp[sample(1:nrow(data.imp), replace = TRUE), ] %>%
    mice(m = 10, 
         maxit = 1,
         method = mod2,
         predictorMatrix = pred,
         where = matrix(TRUE, nrow(.), ncol(.)),
         cp = 1e-32,
         minbucket = 3,
         print = FALSE)
}, .options = future_options(seed = as.integer(123)), .progress = FALSE)

true.fits.imp <- map(1:nsim, ~glm(Outcome ~ BMI + Glucose + Pregnancies,
                                  family = binomial(link = "logit"), 
                                  data = data.imp[sample(1:nrow(data.imp), replace = TRUE),]))

true.fits.imp %>%
  map_dfr(function(x) {
    x %>% 
    broom::tidy(conf.int = TRUE) %>% 
    mutate(cov = conf.low < coef(fit.imp) & coef(fit.imp) < conf.high)
  }) %>% 
  group_by(term) %>%
  summarise(est = mean(estimate),
                 se  = mean(std.error),
                 ciw = mean(conf.high - conf.low),
                 cov = mean(cov)) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

syn2.boot.imp %>%
  map(function(x) {
    x %$% 
      glm(Outcome ~ BMI + Glucose + Pregnancies, 
          family = binomial(link = "logit"))
    }) %>%
  map_dfr(pool3.syn) %>%
  ci_cov(., fit.imp) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

syn2.cp.boot.imp %>%
  map(function(x) {
    x %$% 
      glm(Outcome ~ BMI + Glucose + Pregnancies, 
          family = binomial(link = "logit"))
    }) %>%
  map_dfr(pool3.syn) %>%
  ci_cov(., fit.imp) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```
